\bf Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-08-07 doc/paper.Rmd
major win on the citation front

Methods for matching marks for a variety of tools have been studied in the literature (see \autoref{tab:toolmarks-ER} for an overview):  \citet{manytoolmarks1} and \citet{chumbley} have been analyzing screwdriver marks  digitized using a profilometer;  \citet{manytoolmarks2} have investigated 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope; \citet{afte-chumbley} have been investigated digitized marks from slip-joint pliers generated by a surface profilometer.

>>>>

\hh{changed citation style}
Methods for matching marks for a variety of tools have been studied in the literature (see \autoref{tab:toolmarks-ER} for an overview):  in \cite{manytoolmarks1} and \cite{chumbley} digitized screwdriver marks have been analyzed using a profilometer;  in \cite{manytoolmarks2} 3D marks from screwdriver, tongue and groove pliers captured using a confocal microscope have been investigated; digitized marks from slip-joint pliers generated by a surface profilometer  have been investigated in \cite{afte-chumbley}.

### 2018-08-07 doc/paper.tex
can't get the references to work, but the style file is closer to JFS specs
major win on the citation front

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{hyperref}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

@@

Methods for matching marks for a variety of tools have been studied in
the literature (see \autoref{tab:toolmarks-ER} for an overview):
\citet{manytoolmarks1} and \citet{chumbley} have been analyzing
screwdriver marks digitized using a profilometer; \citet{manytoolmarks2}
have investigated 3D marks from screwdriver, tongue and groove pliers
captured using a confocal microscope; \citet{afte-chumbley} have been
investigated digitized marks from slip-joint pliers generated by a
surface profilometer.

@@

\bibliographystyle{agsm}
\bibliography{bibliography}

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\setcitestyle{numbers}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{adjustbox}
\usepackage{multirow}
\usepackage{subfig}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{hyperref}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

@@

{\textcolor{orange}{changed citation style}}

Methods for matching marks for a variety of tools have been studied in
the literature (see \autoref{tab:toolmarks-ER} for an overview): in
\cite{manytoolmarks1} and \cite{chumbley} digitized screwdriver marks
have been analyzed using a profilometer; in \cite{manytoolmarks2} 3D
marks from screwdriver, tongue and groove pliers captured using a
confocal microscope have been investigated; digitized marks from
slip-joint pliers generated by a surface profilometer have been
investigated in \cite{afte-chumbley}.

@@

\bibliographystyle{vancouver}
\bibliography{bibliography}
